Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-05-02 ms.tex
separated the crystal pattern drawing from the plots

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.49\columnwidth]{crosshatch_zoom.pdf}
\includegraphics[width=.49\columnwidth]{crosshatch_2d_power.pdf}
\caption{
The A5 detector's flat field has a pronounced crosshatch pattern at 23.1$\degree$ , 90.9$\degree$, and 158.6 $\degree$ CCW from the positive X direction.
The crosshatch pattern is visible in a zoom-in of the pixel flat field (left).
The 2D power spectrum of the flat field (right) shows that the angles of the crosshatch pattern are similar to one possible projection of a tetrahedral (zincblende) lattice structure (blue, right).
}\label{fig:crossHatchA5}
\end{figure}

@@

We simulate the effect of this jitter on NIRCam grism time series observations with the following steps:
\begin{itemize}
	\item Fit the existing flat field to an crosshatch model that describes the subpixel behavior
	\item Simulate a PSF using \texttt{webbpsf} \citep{perrin2014webbpsf}
	\item Jitter the simulated PSF over with a 6 mas Gaussian
	\item Bin the simulated images into the native pixel size
	\item Divide by the flat field
	\item Measure the light curve with photometry or spectroscopic aperture
\end{itemize}

>>>>

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.49\columnwidth]{crosshatch_zoom.pdf}
\includegraphics[width=.49\columnwidth]{crosshatch_2d_power.pdf}
\includegraphics[width=.3\columnwidth]{tetrahedral_lattice_projection.png}
\caption{
The A5 detector's flat field has a pronounced crosshatch pattern at 23.1$\degree$ , 90.9$\degree$, and 158.6 $\degree$ CCW from the positive X direction.
The crosshatch pattern is visible in a zoom-in of the pixel flat field (top left).
The 2D power spectrum of the flat field (top right) shows a continuum of frequencies aligned with the three crosshatch angles.
Note the lines in frequency plane are perpendicular to the crosshatch directions in the image plane.
These three angles are similar to one possible projection of a tetrahedral (zincblende) lattice structure of HgCdTe (bottom).
}\label{fig:crossHatchA5}
\end{figure}

The crosshatch pattern is wavelength dependent.

@@

We simulate the effect of this jitter on NIRCam grism time series observations with the following steps:
\begin{itemize}
	\item Fit the existing flat field to an crosshatch model that describes the subpixel behavior
	\item Simulate a PSF using \texttt{webbpsf} \citep{perrin2014webbpsf}
	\item Low frequency ($<$ 1/10second) jitter the simulated PSF over with a 6 mas Gaussian
	\item Bin the simulated images into the native pixel size
	\item Divide by the flat field
	\item Measure the light curve with photometry or spectroscopic aperture
\end{itemize}
